Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-27 paper/paper.Rmd
Small fixes

In the current article, we address the practical barriers of completing replcations as part of required coursework and discuss the methodological decisions that replication projects must address more braodly.  Towards this aim, report the results of replication projects conducted in a graduate-level experimental methods course. Students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.

@@

@@

We begin by describing the details of our course projects to give a sense of what a classroom replication project entails. We then discuss broader decision points for the course design that other instructors might consider. Lastly, we report the results our replications, highlighting the importance of wide-scale replication.

@@

Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen. But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power. Thus, our work here shows what is possible for motivated students using freely-available tools and resources.

@@

That said, we beleive there are many ways to adapt the project format based on the students and constraints of the class.  In Table \ref{tab:classmodels} below, we present mulitple ways in which replication projects may be included in classrooms.  Though we do not go into detail on all of the specifics of what each of these courses might entail, we hope this provides an overview of the possibilities inherent in including replication work as part of student learning.  We next turn to detailed discussion on a few we believe most pertinent to instructors.

@@

Goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Conduct collaborative research} & \multicolumn{1}{p{2in}}{\raggedright Learn best practices and tools} \\

Grouping & \multicolumn{1}{p{2in}}{\raggedright Full Class OR Medium groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individual} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\

Project Selection & \multicolumn{1}{p{2in}}{\raggedright One class replication OR pre-specified list} & \multicolumn{1}{p{2in}}{\raggedright Curated list to choose from} & \multicolumn{1}{p{2in}}{\raggedright Open to student choice*} \\

@@

Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use familiar or GUI tools OR instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach key tool plus introduction of others} & \multicolumn{1}{p{2in}}{\raggedright Teach full set of free open-source software} \\

Review & \multicolumn{1}{p{2in}}{\raggedright Standardized format for submission} & \multicolumn{1}{p{2in}}{\raggedright Group and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\

@@

\end{tabular}
\caption{\label{tab:classmodels} *This can also be done with random selection with sampling criteria} 
\label{tab:classmodels}
\end{table}

@@

The set of studies could be curated more or less for students based on expertise and constraints.  At the other extreme from our small graduate class, in a large undergraduate class it may make logistical sense for the instructors to choose 1-3 replication projects that students can select from. This would allow the instructor to be familiar with all replication projects taking place, and provide more structured discussion and problem-solving based on the challenges groups may run into.

@@

Over half of our students reached out to original authors to request study materials or clafication on methods and/or analysis.  For the purposes of this class, we chose not to require contact with all original authors. Methods and materials should be open to allow for replication and incremental science [@nosek2015], and hoped to make the pedagogical point that good research should not require a researcher to return your email, and make students feel empowered that they can engage with and build on the published literature directly.  That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.  Only in cases where there are issues about access to materials or ambiguities in design/analysis were authors contacted.

However, we acknowledge there are benefits of contacting all authors.  There are two main methods of doing so. First is as a professional courtesy by letting the authors know that their study is being replicated.  This not only provides goodwill (as replication are perceived by some to be adversarial; see Kahneman commentary?), it would also allow the original authors to pre-register their hypotheses or concerns with the replication study as experts in the underlying theory. Second is as a request for methodological feedback prior to replication. This is a trickier issue on many fronts.  By requesting feedback, this perpetuates insider information or lab-specific folklore on methodology that produces the greatest effects. When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science. In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).  In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies. Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.

@@

As much of psychological research is now conducted online, and we know of few PhD programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.  Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.

>>>>

In the current article, we address the practical barriers of completing replcations as part of required coursework and discuss the methodological decisions that replication projects must address more braodly.  Towards this aim, we report the results of replication projects conducted in a graduate-level experimental methods course. Students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*. These studies provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.

@@

We begin by describing the details of our course projects to give a sense of what a classroom replication project entails. We then discuss broader decision points for the course design that other instructors might consider. Lastly, we report the results our replications, highlighting the importance of wide-scale replication efforts.

@@

@@

Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen. But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power. Thus, our work here shows what is possible for motivated students using freely-available tools and resources.

@@

That said, we beleive there are many ways to adapt the project format based on the students and constraints of the class.  In Table \ref{tab:classmodels} below, we present mulitple ways in which replication projects may be included in classrooms.  Though we do not go into detail on all of the specifics of what each of these courses might entail, we hope this provides an overview of the possibilities inherent in including replication work as part of student learning.  We next turn to detailed discussion on a subset of aspects we believe most pertinent to instructors.

@@

Learning Goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Conduct collaborative research} & \multicolumn{1}{p{2in}}{\raggedright Learn best practices and tools} \\

Project Grouping & \multicolumn{1}{p{2in}}{\raggedright Full Class or Medium-sized groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individual} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\

Project Selection & \multicolumn{1}{p{2in}}{\raggedright One class replication or pre-specified list} & \multicolumn{1}{p{2in}}{\raggedright Curated list to choose from} & \multicolumn{1}{p{2in}}{\raggedright Open to student choice*} \\

@@

Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use familiar or GUI tools or instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach key open-source tool plus introduce others} & \multicolumn{1}{p{2in}}{\raggedright Teach full set of free open-source software} \\

Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\

@@

\end{tabular}
\caption{\label{tab:classmodels} The potential models for incorporating replication studies in required coursework. *This can also be done with a systematic sampling strategy} 
\label{tab:classmodels}
\end{table}

@@

The set of studies could be curated more or less for students based on expertise and constraints.  For example, in a large undergraduate class it may be logistical simpler for the instructors to choose 1-3 replication projects that students can select from. This would allow the instructor to be familiar with all replication projects taking place, and provide more structured discussion and problem-solving based on the challenges groups may run into.

@@

Over half of our students reached out to original authors to request study materials or clafication on methods and/or analysis.  For the purposes of this class, we chose not to require contact with all original authors. We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to make students feel empowered that they can engage with and build on the published literature directly.  That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.  Only in cases where there were issues about access to materials or ambiguities in design or analysis were authors contacted.

However, we acknowledge there are benefits of contacting all original authors.  There are two main methods of doing so. First is as a professional courtesy by letting the authors know that their study is being replicated.  This not only provides goodwill (as replication are perceived by some to be adversarial; see Kahneman commentary?), it would also allow the original authors to pre-register their hypotheses or concerns with the replication study as experts in the underlying theory. Second is as a request for methodological feedback prior to replication. This is a trickier issue on many fronts.  By requesting feedback, this perpetuates insider information or lab-specific folklore on methodology that produces the greatest effects. When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science. In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).  In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies. Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.

@@

As much of psychological research is now conducted online and we know of few graduate programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.  Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.

### Sample size and power analyses
